---
title       : Linear regression - excercise 
subtitle    : Developing data products - projects
author      : sta1111 #landslide 
framework   : landslide       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides


---

## Linear regression - exercise 
# Developing data products - projects

The main purpose of she presentation is to show steps of fitting linear model.
The analysis is prepared on _mtcars_ dataset showed on the second slide and the depending variable is _mpg_. The following slides consists of:
- plot with influence of combination of dependent variables on R2
- formula od chosen model - with variables that implies the highest R2 + estimated coefficients
- plots that help to asses goodless of fit to real data

--- .class #id 

## mtcars dataset table

```{r, echo=FALSE, warning=FALSE, comment="" }
library("leaps")
dataset <- mtcars
dataset[1:16,]
```

---

## Variable Selection

```{r}
leaps<-regsubsets(mpg ~ ., data=dataset,nbest=10)
plot(leaps,scale="r2")

```

---

## Linear model estimation

```{r, echo=FALSE, warning=FALSE, comment=""}
fit <- lm(mpg ~ disp + hp + drat + wt + qsec + am + gear + carb, data=dataset)
fit$call
fit$coefficients

```

---

## Goodness of fit

```{r, echo=FALSE}
layout(matrix(c(1,2,3,4),2,2)) 
plot(fit)

```

